Job Demands-Resources model components through the lens of O*NET classifications

### 2022-01-26 Submission.Rmd
Edits after first meeting of the semester

abstract: |
  O\*NET work characteristics were rated in terms of relevance, perception of demand, and perception as resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus & Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.

@@

>*Research Question 4*: Which O\*Net job characteristics show wide variability in assigned JD-R classification of resource, challenge, or hinderance.

>>>>

abstract: |
  O\*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus & Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.

@@

>*Research Question 4*: Does the **type of work** reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?

### 2022-01-26 Submission.tex
Edits after first meeting of the semester

\abstract{
O*NET work characteristics were rated in terms of relevance, perception of demand, and perception as resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus \& Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.

@@

In an attempt to integrate the O*NET taxonomy within the orientation of the Job Demands-Resources (Bakker et al., 2003; Bakker \& Demerouti, 2017; Demerouti et al., 2001), a series of evaluations were made that used: 1) O*NET terminology (both descriptor and response option), 2) JD-R influenced ratings of demand, challenge, or hindrance. The outcome of this integration is a cross-walk between the Department of Labor classifications and the I-O literature steeped JD-R. While O*Net provides thorough documentation of information associated with job analyses, one of the remaining limitations is its lack of connection to theory. Given the popularity of the Job Demands-Resources Theory (JD-R; Demerouti et al., 2001) in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net. In an attempt to integrate the O*Net taxonomy within the orientation of the JD-R framework (Bakker et al., 2003; Bakker \& Demerouti, 2017; Demerouti et al., 2001), a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance. Prior to a description of results, a brief overview of both the JD-R theory and O*Net is provided.

@@

@@

Interestingly, we have not yet integrated this practical and accessible resource within the JD-R framework. This paper aims to provide such a crosswalk or integration of the theory and practical occupations-focused data on O*Net. Several broad research questions are examined across jobs:

@@

\hypertarget{alternatively-alicias-jdr-vs-stress-model-predictions}{%
\subsection{ALTERNATIVELY, Alicia's JDR vs stress model predictions}\label{alternatively-alicias-jdr-vs-stress-model-predictions}}

Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal

@@

\leavevmode\hypertarget{ref-bakker2017job}{}%
Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.

>>>>

\abstract{
O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus \& Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.

@@

Given the popularity of the Job Demands-Resources Theory (JD-R; Demerouti et al., 2001) in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net. A series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.

@@

\hypertarget{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}{%
\subsection{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}

@@

This paper aims to provide an integration of the theory and practical occupations-focused data on O*Net. Several broad research questions are examined across jobs:

@@

@@
